Fast Sorting on Modern Computers

### 2005-08-30 docs/tech_report/quick.tex
filled in 25% reference

LaMarca notes that quicksort is already very cache efficient\footnote{We
speculate wildly at this point and suggest that since an average of 25\% of
computing time is spent sorting (see \cite{TODO}), the development of caches has
been subconsciously affected by the cache performance of quicksort.}, as it has
excellent spatial and temporal locality. Once it no longer fits in the cache,
however, the number of misses should increase significantly. This is especially
true in the case of the base quicksort, which does an insertion sort across then
entire array at the end.

>>>>

LaMarca notes that quicksort is already very cache efficient\footnote{We
speculate wildly at this point and suggest that since, historically, an average
of 25\% of computing time has been spent sorting (see \cite[Page 3]{Knuth97}),
the development of caches has been subconsciously affected by the cache
performance of quicksort.}, as it has excellent spatial and temporal locality.
Once it no longer fits in the cache, however, the number of misses should
increase significantly. This is especially true in the case of the base
quicksort, which does an insertion sort across then entire array at the end.
